\documentclass[10pt]{article}

\usepackage[usenames]{color} %used for font color
\usepackage[a4paper, total={7in, 11in}]{geometry}
\usepackage{pifont}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage{multicol}

\setcounter{secnumdepth}{0} % remove section numbering
\setlist[itemize]{noitemsep,left=0pt .. \parindent}

\titlespacing{\subsection}{0pt}{*0}{*0} % remove vertical spacing above and below
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\small \bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\small \itshape}

\pagestyle{empty} % remove page number
\pdfgentounicode=1

\begin{document}

\begin{center}
	\begin{minipage}{0.5\textwidth}
		{\bfseries \Large
			PURNA CHANDRA SAHU % Name Here
		} \\ 
		Assistant Manager-Risk Advisory \\ % Title [optional] 
		SAP Security \& GRC

	\end{minipage} \hfill
	\begin{minipage}{0.3\textwidth}
		\footnotesize \raggedright
			\faEnvelope { purna.chandra.1618@gmail.com }\\
			\faPhone { +91-9556572845} \\
			\faIcon{linkedin} \href {linkedin.com/in/purna-chandra-sahu}{purna-chandra-sahu} \\
			\faIcon{github}  \href {github.com/pc-purna}{pc-purna} \\
			\faPassport {Passport: \textit Z3466886}
	\end{minipage}
\end{center}

\section{Profile Summary}
%=================%
\begin{minipage}{1.0\textwidth}
	
	\small 
	{
		Purna Chandra brings in over 5.8 years of IT experience and is currently Assistant Manager 
	in Risk Advisory practice of Deloitte India. His experience spans across SAP Security \& GRC. 
	Specialized in SAP GRC Access controls, SAP ECC, S4HANA, Fiori \& BI Security concepts and 
	worked on Implementation projects and Managed Services.
	}
\end{minipage}



\section{Work Experience}
%=================%
\subsection{Deloitte Touché Tohmastu India LLP \hfill \normalfont Bengaluru, Karnataka}
\subsubsection{Assistant Manager-Risk Advisory \hfill  Oct 2022 - Present \\}
\begin{itemize}
	\small
    	\item[] \textbf{\underline{SAP GRC:}}
			\item Experience in E2E Access Control implementation [ARA, EAM, ARM, BRM, UAR and SOD risk review modules].
			%\item In depth implementation/configuration experience in ARA, EAM, ARM, BRM, UAR and SOD risk review modules.
			\item Experience in creating test scripts for the above-mentioned GRC AC modules.
			%\item Experience in the Post Installation configuration for GRC AC involving configuration of Parameters, Connectors.
			\item Experience in design, analysis and build of SAP GRC SoD ruleset - worked on Mitigation controls, Risks and Functions.
			\item SAP SuccessFactors and SAP ECP integration with SAP GRC for Cross-system risk analysis and access provisioning.
			%\item Assessment on custom transaction inclusion in SOD ruleset and inclusion for role design.
			%\item Knowledge on analysis of SOD risk with associated Transaction code.
			\item Experience in configuring and enhancing FF Log review workflow involving analysis of SOD and Critical actions.
			\item Experience in SAP GRC RM configuration and master data creation.
\end{itemize}

\begin{itemize}
	\small
    	\item[] \textbf{\underline{SAP S4HANA/Fiori:}}
			\item Fiori Catalog and Group creation for S4HANA; Fiori Spaces and Pages creation for S4HANA
			%\item Fiori Spaces and Pages Design as per Business Roles.
			\item Activation of OData services SICF nodes.
			\item Fiori role building and SU24 authorisation maintenance.
			\item Fiori Application issue troubleshooting using IWFND/ IWBEP Error logs, Brower console and application logs.
\end{itemize}

\begin{itemize}
	\small
    	\item[] \textbf{\underline{SAP ECC:}} 
			\item GRC access control - EAM relevant SPRO configuration.
    		\item Master data/testing scenario creation for FF Log Review workflow.

%Client Information - Deloitte.%
		
    \begin{itemize}
        \item[]  
        	\item[\ding{226}] \textbf {Client:} Unilever, India
        	\item[] \textbf {Environment: } SAP GRC AC 12.0, SAP ECC
    \end{itemize}
    
    \begin{itemize}
        \item[] \textbf {Key Responsibility:}
        	\item GRC EAM configuration and master data preparation.
        	\item FF Log review workflow enhancement – Made relevant MSMF workflow changes.
    		\item Test script creation and E2E testing on FF Log review workflow.
    \end{itemize}  
     
    \begin{itemize}
        \item[]  
        	\item[\ding{226}] \textbf {Client:} Cameco, Canada
        	\item[] \textbf {Environment: } SAP GRC AC 12.0, SAP S4HANA, SAP ECP, SAP SuccessFactors
    \end{itemize}

    \begin{itemize}
        \item[] \textbf {Key Responsibility:}
			\item SAP GRC Access Control E2E Implementation.
			\item Cross system risk analysis for SAP SFEC, S4 and ECP - Configuration and SoD Ruleset built.
			\item SAP SFEC and SAP ECP integration with SAP GRC 12 embedded in SAP S4HANA.
			%\item Requirement gathering and Workshops from Client on SAP GRC configuration.
			\item S4HANA Role building, Fiori App customisation – Fiori Catalogs \& Group.
			\item Fiori App Authorisation issue troubleshooting.
    \end{itemize}
     
    \begin{itemize}
        \item[]  
			\item[\ding{226}] \textbf {Client:} Ashok Leyland, India
			\item[] \textbf {Environment: } SAP GRC AC 12.0, SAP ECC
    \end{itemize}

    \begin{itemize}
        \item[] \textbf {Key Responsibility:}
			\item SAP GRC AC Implementation.
			\item SAP GRC RM Implementation – SPRO configuration and Master Data preparation.
			%\item Requirement gathering and Workshops with Client on SAP GRC configurations.
    \end{itemize}
\end{itemize}

\titlerule {\ }{}{}
%Client Information - IBM.%

\subsection{IBM India Pvt. Ltd \hfill \normalfont Kolkata, West Bengal}
\subsubsection{Package Specialist - SAP Security \& GRC \hfill  July 2018 - October 2022 \\}

	\begin{itemize}
		\small
     		\item[] \textbf{\underline{SAP ECC, ISU, C4C, Fiori:}} 
     			\item Experience in design and building of SAP PFCG roles as per business requirement.
				\item Experience in maintenance of User Master Records, Authorization Groups/Profiles/Roles to R/3 users.
				\item Authorisation Object Maintenance using SU24.
				%\item Created and maintained Authorization Groups for Tables, Reports and assigned them accordingly.
				\item Analyse and troubleshoot security issues using SU53, ST01, STAUTHTRACE, SLG1 and SUIM.
				\item Experience with SECATT scripts for mass password creation in ECC, role assignment and SODA limit assignment.
				\item Worked with CUA and Non-CUA Environments. Knowledge about %implementing
					CUA configuration over the SAP landscape.
				\item Worked in SAP Support portal for managing OSS, Developer Access key \& Object access key creation.
				\item Performed Monthly House-keeping clean-up activities.
	\end{itemize}

	\begin{itemize}
		\small
     		\item[] \textbf{\underline{SAP GRC:}} 
        		\item Worked on GRC ARA, EAM, ARM modules.
				%\item Worked on EAM configuration and EAM Master data maintenance.
				\item Risk Analysis during Role build and User access assignment. 
				\item Report extraction for audit and re-certification activities.
	\end{itemize}

	\begin{itemize}
		\small
     		\item[] \textbf{\underline{SAP BI /BW:}} 
        		\item Build Analysis Authorizations using the transaction RSECADMIN and Role maintenance.
				\item Troubleshoot analysis authorizations related problems using RSECADMIN.
	\end{itemize}

	\begin{itemize}
		\small
     		\item[] \textbf{\underline{SAP BOBJ:}} 
        		\item User administration and access assignment to end users as per requirement.
				\item Performed Monthly House-keeping clean-up activities.
	
%Client Information - IBM.%
		\begin{itemize}
		\item[]  
			\item[\ding{226}] \textbf {Client:} Thames Water Utilities Ltd, UK
			\item[] \textbf {Environment: } SAP ECC 6, ISU, C4C, GRC AC (10.1,12), Fiori, BI 7, CRM
		\end{itemize}
		
		\begin{itemize}
			\item[] \textbf {Key Responsibility:}
				\item Provided production and non-production support for various SAP systems such as SAP ECC, ISU, BI/BW, C4C, GRC, Fiori, and CRM.
				\item Supported for SAP Security controls and User Access Reviews process, conducted SOD and user access analysis under Risk Analysis and Remediation.
				\item Authorization object maintenance in SU24.
				\item Supported in audits performed by client and external vendors.
				\item Performed critical analysis on EWA reports from SAP Security perspective produced monthly or quarterly.
				\item Worked in Migration Activities from SAP Security perspective and managed Team Members for the same for Project deliveries.
				\item SAP License Audit: Usage of SLAW2 and USMM to extracting SAP Licence usage in the systems and provide the consolidated report to external and SAP auditors.
				\item Perform KT sessions for the new Joiners in the Team and guide them about Project activities from SAP Security perspective.
		\end{itemize}
	\end{itemize}

\section{Education}
%=================%
	\subsection {International Institute of Information Technology \hfill \normalfont Bhubaneswar}
	\subsubsection   { \normalfont \small \textbf{Course:} Bachelor of Technology, Computer Science and Engineering  \hfill \raggedright August 2014-June 2018}
	\begin{itemize}
		\small
			\item Cumulative GPA: 8.02
	\end{itemize}

	\subsection {Vyomayana Samstha Vidyalaya \hfill \normalfont Sunabeda}
	\subsubsection   { \normalfont \small \textbf{Course:} Senior Secondary School $|$ 12th Grade(CBSE)  \hfill \raggedright April 2013–June 2014}
	\begin{itemize}
		\small
			\item Percentage: 91.2 \%
	\end{itemize}
	
	%\subsection {Vyomayana Samstha Vidyalaya \hfill \normalfont Sunabeda}
	\subsubsection   { \normalfont \small \textbf{Course:} Secondary School $|$ 10th Grade(CBSE)  \hfill \raggedright April 2011–June 2012}
	\begin{itemize}
		\small
			\item Cumulative GPA: 10.0
	\end{itemize}


\section{Skills \& Interests}
%===========================%
\begin{description}[itemsep=0pt]
	\small
		\item[Industry Served:] Energy \& Utilities; Consumer Products
		\item[SAP Applications:] GRC 10.1 \& 12.0, S4HANA, ECC, Fiori, ISU, C4C, HANA, BW, BOBJ
		\item[Trainings:] SAP Security; SAP GRC(AC, PC, RM);SAP HANA Security; SAP BTP(Basic)
		\item[Tools used:] Transport Expresso; Azure DevOps; HP ALM; Service Now; Octane ALM
		\item[Language:] C, C++, Java, Python, SQL
		\item[Interests:] Problem-solving, Analytics, Cybersecurity, Data Science, Cyptography
\end{description}

\section{SPECIALIZATION}
%=================
\begin{itemize}
	\small
		\item SAP GRC Access Control (10.1, 12.0)
		\item SAP Security - User \& Role Administration
		%\item SAP Role Design
		\item SAP Implementation and Managed services
\end{itemize}

\section{Certifications}
%===============================%
\begin{enumerate}[label=\null, left=0pt..0pt, itemsep=0pt]
	\small
		\item SAP Certified Application Associate SAP Access Control 12 \hfill July 2022
		\item AWS Cloud Practitioner Certification \hfill August 2021-August 2024
		\item Energy \& Utilities Industry Foundations \hfill March 2019
\end{enumerate}

\section{Achievements}
%===============================%
\begin{enumerate}[label=\null, left=0pt..0pt, itemsep=0pt]
	\small
		\item Got multiple Recognition Awards at Deloitte.
		\item Got multiple Manager's Choice Awards at IBM.
		\item Got Spark Award - Cash Reward for being the Top performer in project at IBM.
\end{enumerate}

\end{document}\begin{document}
$$
\end{document}